---
title: "lab30"
author: "Andrew Do"
date: "August 1, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
setwd("~/Desktop/Stats R/stat133-su2016/29-lesson-sql")
chinook <- src_sqlite("Chinook_Sqlite.sqlite")
```

## SQL Lab

This lab will not be graded.  It is meant to give you some practice with using SQL.  You'll need to open a connection to the `chinook` database.

1.  Which tracks are more expensive than $0.99?
```{r}
chinook %>% tbl(sql("
  SELECT 
    Name 
  FROM 
    Track 
  WHERE 
    UnitPrice > 0.9
"))
```

2.  Which tracks have the word 'love' in the title?
```{r}
chinook %>% tbl(sql("
  SELECT 
    Name
  FROM
    Track
  WHERE
    Name LIKE '%love%'
"))
```

3.  Which tracks begin with the word 'love'?
```{r}
chinook %>% tbl(sql("
  SELECT 
    Name
  FROM 
    Track 
  WHERE 
    Name LIKE 'love%'
"))
```

4.  Which tracks were composed by Jimi Hendrix
```{r}
chinook %>% tbl(sql("
  SELECT 
    Name 
  FROM 
    Track 
  WHERE 
    Composer = 'Jimi Hendrix'
"))
```

5.  Which albums are by Queen?
```{r}
chinook %>% tbl(sql("
  SELECT
    Name, 
    Title
  FROM
    Artist 
    LEFT JOIN Album ON Album.ArtistId = Artist.ArtistId 
  WHERE
    Name = 'Queen'
"))
```

6.  Who is the album Zooropa by?
```{r}
chinook %>% tbl(sql("
  SELECT 
    Name
  FROM 
    Artist
    LEFT JOIN Album ON Album.ArtistId = Artist.ArtistId
  WHERE 
    Title = 'Zooropa'
"))
```

7.  Which tracks are by Amy Winehouse?
```{r}
chinook %>% tbl(sql("
  SELECT
    Artist.Name, 
    Album.Title, 
    Track.Name 
  FROM Artist
    INNER JOIN Album ON Album.ArtistId = Artist.ArtistId
    INNER JOIN Track ON Album.AlbumId = Track.AlbumId
  WHERE Artist.Name = 'Amy Winehouse'
"))
```

8.  Which tracks are on the playlist Brazillian Music and who are they by?
```{r}
chinook %>% tbl(sql("
  SELECT 
    Playlist.Name, 
    Track.Name 
  FROM Playlist
    INNER JOIN PlaylistTrack ON PlaylistTrack.PlaylistId = Playlist.PlaylistId
    INNER JOIN Track ON PlaylistTrack.TrackId = Track.TrackId
  WHERE Playlist.Name = 'Brazilian Music'
"))
```

9.  How many songs are on each playlist? Keep the playlist names and order by number of songs.
```{r}
chinook %>% tbl(sql("
  SELECT 
    Playlist.Name, 
    count(*) 
  FROM PlaylistTrack
    INNER JOIN Playlist on Playlist.PlaylistId = PlaylistTrack.PlaylistId
  GROUP BY PlaylistTrack.PlaylistId
  ORDER BY count(*) DESC
"))
```

10.  How expensive are each of Amy Winehouse's albums?
```{r}
chinook %>% tbl(sql("
  SELECT 
    Artist.Name, 
    Album.Title, 
    SUM(Track.UnitPrice) 
  FROM 
    Artist
    INNER JOIN Album on Album.ArtistId = Artist.ArtistId
    INNER JOIN Track on Album.AlbumId = Track.AlbumId
  WHERE Artist.Name = 'Amy Winehouse'
  GROUP BY title
"))
```