---
title: "Untitled"
author: "Shangjun Jiang"
date: "August 3, 2016"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(networkD3)
library(jsonlite)
library(magrittr)
library(readr)
library(purrr)
library(dplyr)
#setwd("~/Dekstop/Stats R/githubrepos-jennyjiang95/labs9")

#setwd("~/Desktop/Stats R/githubrepos-jennyjiang95/labs9")
```

To create a simple force-directed network diagram with the `networkD3` package, you need a data frame containing the edges of your network stored as a data frame.  The first column of the data frame should be `source` and the second, `target`, denoting the nodes where the edges start and end, respectively.
```{r}
# Create fake data
src    <- c("A", "A", "A", "A",
            "B", "B", "C", "C", "D")
target <- c("B", "C", "D", "J",
            "E", "F", "G", "H", "I")
networkData <- data.frame(src, target)
```

Once you have the data frame, the process is rather straightforward.  You simply supply the data frame to `simpleNetwork`.
```{r}
# Plot
simpleNetwork(networkData)
```

Customizing properties of the network is as easy as supplying additional arguments.
```{r}
simpleNetwork(
  networkData, 
  width = 400,
  height = 250,
  textColour = "orange",
  linkColour = "blue",
  nodeColour = "pink", 
  opacity = 0.9
)
```

To get even more control over the the network (such as specifying how close the nodes should be to one-another), you would use `forceNetwork`.  This takes on two data frames: `links` and `nodes`.

* `links` should be a 2-3 column data frame containing information on the edges of the network:
    + `source` and `target` denote the same information as above; however, the information should be encoded as indices starting from 0
    + an optional `value` column specifies how wide the edges should be (this will be scaled relatively by the graphing algorithm)
* `nodes` is a 1-4 column data frame containing vertex information
    + `name` should contain the names of the nodes
    + `nodeid` numbers that reference the indices in `links`.  If this isn't specified, then the algorithm will assume the order that appears in `links$source`
    + `group` groupings for the nodes
    + `nodesize` how large each node should be

```{r}
miserables <- fromJSON("miserable.json")
miserables %$%
  forceNetwork(
    Links = links, 
    Nodes = nodes, 
    Source = "source",
    Target = "target", 
    Value = "value", 
    NodeID = "name", 
    Group = "group", 
    opacity = 0.4
  )
```

`sankeyNetwork` works the same way, except that it plots a [Sankey Flow Diagram](https://en.wikipedia.org/wiki/Sankey_diagram) instead.

```{r}
fromJSON("energy.json") %$%
  sankeyNetwork(
    Links = links,
    Nodes = nodes,
    Source = "source",
    Target = "target",
    Value = "value",
    NodeID = "name",
    units = "TWh",
    fontSize = 12,
    nodeWidth = 30
  )
```

A `radialNetwork` models a tree, which is a network that has a root node and no cycles.  The `List` argument is a list of lists (of lists...) with elements named `name` and `children`.  It's much easier to think of the data in JSON format.
```{r}
flare <- fromJSON("flare.json", simplifyDataFrame = FALSE) 
radialNetwork(List = flare, fontSize = 10, opacity = 0.9)
```

The above plot has too much information in a small space.  We should subset for readability.
```{r}
flareSubset <- flare
flareSubset$children <- flareSubset$children[1:3]
radialNetwork(List = flareSubset, fontSize = 10, opacity = 0.9)
```

An alternate way of displaying the tree would be with a diagonal network.  I'm not sure why it's called diagonal when it's clearly displayed in a horizontal fashion.
```{r}
diagonalNetwork(List = flareSubset, fontSize = 10, opacity = 0.9)
```

## Exercises
As usual, the hardest part about working with data is getting it into the right form.

### Read Highland Tribes (easy)
Hage & Harary (1983) use the Gahuku-Gama system of the Eastern Central Highlands of New Guinea, described by Read (1954), to illustrate a clusterable signed graph. Read's ethnography portrayed an alliance structure among three tribal groups containing balance as a special case; among Gahuku-Gama the enemy of an enemy can be either a friend or an enemy.

The signed graph has been split into two matrices: GAMAPOS for alliance ("rova") relations, GAMANEG for antagonistic ("hina") relations. To reconstruct the signed graph, multiply GAMANEG by -1, and add the two matrices.

The data are stored in `read_headlands.dat`, and can be read in with `read_delim` (skipping lines to avoid the header!).


```{r}
headlands <- read_delim("read_headlands.dat",
                delim = "")


```


### Siphonophorae (hard)
The [siphonophorae](https://en.wikipedia.org/wiki/Siphonophorae) phylogeny is shown as a force-directed network below.  Massage the data so that it can be displayed as a radial network.
```{r}
siphon <- fromJSON("siphonophorae.json")
siphon %$%
    forceNetwork(
    Links = links, 
    Nodes = nodes, 
    Source = "source",
    Target = "target", 
    Value = "value", 
    NodeID = "name", 
    Group = "group", 
    opacity = 0.4
  )
```
