---
title: "Berkeley Police Data"
author: "Amy Zhu; Mengyu Li; Rebecca Reus; Shangjun Jiang"
date: "August 7, 2016"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sp)
library(ggmap)
library(tidyr)
library(readr)
library(plyr)
library(dplyr)
library(ggvis)
library(tidyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(data.table)
library(rworldmap)
library(maps)
library(mapdata)
library(maptools)
library(scales)
library(RgoogleMaps)
library(tmap)
library(sp)
library(rgdal)
library(rgeos)
library(RColorBrewer)
library(grid)
library(gridExtra)
```


## Introduction

 For the final project, our group cleaned, explored, and analyzed four different data sets from the City of Berkeley that contained information on stops, calls for service, arrests, and jail bookings made by the the police department in 2016 (and 2015 as well for the stop data). Rather than limiting the project to one set of data, three sets were chosen in order to gain a more holistic and comprehensive understanding of the data. The additional variables included expanded the project’s capacity for manipulating data, examining relationships, and improving result reliability. 

#### Data Collection

* [Stop Data (16,000)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Stop-Data/6e9j-pj9p)
* [Arrest (200)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Log-Arrests/xi7q-nji6)
* [Jail Bookings (250)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Log-Jail-Bookings/7ykt-c32j)
* [Calls for Service (4,000)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Calls-for-Service/k2nh-s5h5)
* [Berkeley Census Data](https://data.cityofberkeley.info/Demographics/Census-Data-2000-And-2010/bnkq-f2ge)
*[Census 2010 Population and race data by county by census tract](http://www.bayareacensus.ca.gov/small/small.htm)


With the variety of resources and information made available by collating multiple data sets, the objective for the project was to study differences in police activity (in terms of call requests and patrols) and intensity of assessed offenses based on time, race, gender, age, and mental health. As a challenge, another project target was to create a map applet depicting the density of police activity in Berkeley with an interactive component allowing the visitor to input an address and observe their proximity and observe the types of incidences that occurred most commonly in the area. 

For the stop data, there were 16,255 incidents assessed by the Berkeley police. In each case, the call date and time, location, incident type, and disposition(s) were recorded. The cases typically had a six character disposition, with each character conveying race, gender, age, reason, enforcement, and car search,  respectively, for each subject involved in the incident, although there were additional dispositions, ranging from one to three characters,  that could be input and conveyed other information. In order to prepare the data for exploration, the cleaning process included changing the call date and time to the lubridate format, transforming the addresses into longitude and latitude referencing Google Maps, and separating the information on dispositions into separate row entries for each individual assessed in a case and splitting it further by isolating “other” and six character dispositions into different columns.

The data for arrests (205), and jail bookings (223) contained similar information on case/arrest/booking number, date and time, type, and subject information (name, race, sex, D.O.B., age, height, weight, hair, eyes, and occupation) and statute information (type, description, agency, and disposition). Cleaning required the dates and times to be put into lubridate format, for the two data sets to be compiled in a reasonable, and for other needed adjustments. The same code created for the stop data would be used again to convert address information to longitudinal and latitudinal coordinates. 


## Data Analysis

```{r, echo=FALSE, include = FALSE, message=FALSE, warning = FALSE}
# Read data

############################## stop data ############################## 
stop_by <- read_csv("cleaned_stop_data.csv")

stop_by$Call.Date.Time <- mdy_hm(stop_by$Call.Date.Time)
stop_by$AgeRange <- as.factor(stop_by$AgeRange)

stop_by <- stop_by %>%
  mutate(Hour = as.integer(hour(Call.Date.Time))) %>%
  mutate(Day = as.factor(as.integer(wday(Call.Date.Time))))

stop_by$Race<- stop_by$Race %>% 
  str_replace("A", "Asian") %>% 
  str_replace("B", "Black") %>% 
  str_replace("H", "Hispanic") %>% 
  str_replace("O", "Other") %>% 
  str_replace("W", "White")

stop_by$Gender<- stop_by$Gender %>% 
  str_replace("F", "Female") %>% 
  str_replace("M", "Male") 

stop_by$Reason <- stop_by$Reason %>% 
  str_replace("I", "Investigation") %>% 
  str_replace("T", "Traffic") %>% 
  str_replace("R", "Reasonable Suspicion") %>% 
  str_replace("R", "Probation/ Parole") %>% 
  str_replace("W", "Wanted")

stop_by$Enforcement <- stop_by$Enforcement %>% 
  str_replace("A", "Arrest") %>% 
  str_replace("C", "Citation") %>% 
  str_replace("O", "Other") %>% 
  str_replace("W", "Warning")

stop_by$CarSearch <- stop_by$CarSearch %>% 
  str_replace("S", "Search") %>% 
  str_replace("N", "No Search")


############################## location data ############################## 
mergedf <- readRDS( 'StopData_merged.rds' )

## Location info:
latmax <- max(mergedf$lat, na.rm = TRUE) 
latmin <- min(mergedf$lat, na.rm = TRUE)
lonmax <- max(mergedf$long, na.rm = TRUE) 
lonmin <- min(mergedf$long, na.rm = TRUE)
latvals <- c(latmin, latmax)
lonvals <- c(lonmin, lonmax)

## Make the variables factors:
mergedf$CarSearch <- factor(mergedf$CarSearch)
levels(mergedf$CarSearch) <- c("No Search", "Search")  

mergedf$Race <- factor(mergedf$Race)
levels(mergedf$Race) <- c("Asian", "Black", "Hispanic", "Other", "White")

mergedf$Enforcement <- factor(mergedf$Enforcement)
levels(mergedf$Enforcement) <- c("Arrest", "Citation", "Other", "Warning")

mergedf$Reason <- factor(mergedf$Reason)
levels(mergedf$Reason) <- c("Other", "Investigation", "Probation/Parole", "Reasonable Suscipcion", "Traffic", "Wanted")

mergedf <- mergedf %>%
  mutate(Arrest = ifelse( 
    as.character(Enforcement) == "Arrest", 
    "Arrested",
    "Not Arrested") ) %>%
  mutate(Arrest = factor(Arrest))

v <- factor(mergedf$Other)

mergedf <- mergedf %>%
  mutate(Emergency.Psych.Eval = ifelse( str_detect(as.character(Other), "MH"), 
                                        yes = "Yes",
                                        no = "No") )

mergedf$Emergency.Psych.Eval <- factor(mergedf$Emergency.Psych.Eval)

### BerkeleyMap 
berkMap = map = get_map(location = c(lon = mean(lonvals), lat = mean(latvals)), zoom = 14)


############################## census data ############################## 

blocks <- readOGR("Census_Tract_Polygons2010","Census_tracts_2010", verbose = TRUE)

locationCensusFiles <- "Census_Tract_Polygons2010"
blocks <- readOGR(locationCensusFiles,"Census_tracts_2010", verbose = TRUE)
b2 <- spTransform(blocks, CRS("+proj=longlat +datum=WGS84"))
b3 <- fortify(b2)

############################## arrest data ############################## 
arrest <- read.csv("Berkeley_PD_Log_-_Arrests.csv")

############################## jail data ############################## 
jail <- read.csv("Berkeley_PD_Log_-_Jail_Bookings.csv")


############################## multiplot function ############################## 
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


We found the census data from the Berkeley open data website and created a headmap of the Berkeley population. Similarly, we created a heat map based on the stop data.  Interestingly, we found that the most dense place (around north Berkeley) is a relatively safe place. The place where people are more likely to be stopped (downtown berkeley area) is less dense. Since Downtown Berkeley area is a transportation hub, numerous people come and go around this area. Though there are more people living north Berkeley, mainly residents will visit the area. Therefore, the most likely place to get stopped is not the most dense living place. 

### Heat Map 1: Berkeley Census data.
```{r, fig.width=10, fig.asp=0.8, echo=FALSE}
ggmap(berkMap) +
  stat_density2d(aes(x = long, y = lat, fill= ..level.., alpha = .2* ..level..),
    size = 2, bins = 5, data = b3, geom = "polygon") +
  scale_fill_gradient(low = "black", high = "red") +
    theme (panel.grid.major = element_blank (), # remove major grid
		       panel.grid.minor = element_blank ()  # remove minor grid
		       ) + 
  ggtitle("Population Density") +
  labs(alpha = element_blank())+
  guides(alpha = FALSE)
```

### Heat Map 2: All BPD Stops Density, 2015-2016
```{r, fig.width=10, fig.asp=0.8, echo=FALSE}
# a contour plot
ggmap(berkMap) +
  stat_density2d(aes(x = long, y = lat, fill= ..level.., alpha = .2* ..level..),
    size = 2, bins = 5, data = mergedf, geom = "polygon") +
  scale_fill_gradient(low = "black", high = "red") +
    theme (panel.grid.major = element_blank (), # remove major grid
		       panel.grid.minor = element_blank ()  # remove minor grid
		       )+ 
  ggtitle("All BPD Stops Density, 2015-2016") +
  labs(alpha = element_blank())+
  guides(alpha = FALSE)

```

Then we explored the stop data by age range (0-18; 18-29; 30-39; and 40+) and data. Similar to the all stop data density, the area that is most likely to be stopped is the same: Downtown Berkeley. The differences in age range and race don't play a crucial role in the possibility of being stopped in Berkeley. These two analysis confirmed our explanations for the all stop data heat map. 

### Heat Map 3: BPD Stop Contour Map of Berkeley by Age Range
```{r, fig.height = 8, fig.width = 10, echo=FALSE}
ggmap(berkMap) +
  stat_density2d( aes(x = long, y = lat, fill = ..level.., alpha = ..level..),
    bins = I(5), geom = "polygon", data = mergedf ) +
  scale_fill_gradient2( "Stop Density",
    low = "white", mid = "orange", high = "red", midpoint = 25) +
  labs(x = "Longitude", y = "Latitude") + facet_wrap(~ AgeRange) +
  scale_alpha(range = c(.2, .55), guide = FALSE) +
  ggtitle("BPD Stop Contour Map of Berkeley by Age Range") +
  guides(fill = guide_colorbar(barwidth = 1.5, barheight = 10))
```

Note: 1 refers to age 0-18; 2 refers to age 18-29; 3 refers to age 30-39; and 4 refers to age 40+.


## Heat Map 4: BPD Stop Contour Map of Berkeley by Race
```{r, fig.height = 5, fig.width = 10, echo=FALSE}
ggmap(berkMap) +
  stat_density2d( aes(x = long, y = lat, fill = ..level.., alpha = ..level..),
    bins = I(5), geom = "polygon", data = mergedf ) +
  scale_fill_gradient2( "StopDensity",
    low = "white", mid = "orange", high = "red", midpoint = 100) +
  labs(x = "Longitude", y = "Latitude") + facet_wrap( ~ Race ) +
  scale_alpha(range = c(.2, .55), guide = FALSE) +
  ggtitle("BPD Stop Contour Map of Berkeley by Race") +
  guides(fill = guide_colorbar(barwidth = 1.5, barheight = 10))
```

The Berkeley PD stop data reflects accidents that have been visited by the Berkeley Police Department. After the initial exploration of the Berkeley stop data, we focus on on the information provided by the dispositions variable. The dispositions variable provides information on race, gender and age range, stop reason and enforcement of the stop, the car search information during the stop, and additional dispositions.


### Analysis of Race
#### Picture: count of person recorded in each race
```{r, echo=FALSE}
stop_race <- stop_by %>%
  ggvis(x = ~Race , fill = ~AgeRange) %>%
  layer_bars() %>%
  add_tooltip(function(stop_by) stop_by$AgeRange)

stop_race
```

####Table: count of person recorded in each race

   Race     | Count | 0-18 | 18-29 | 30-39 | 40+
----------  |------ |------|-------|-------|-------
A (Asian)   | 1141  | 8.50%| 43.47%| 21.03%| 26.99%
B (Black)   | 4636  | 2.29%| 34.97%| 25.09%| 37.66%
H (Hispanic)| 1676  | 3.22%| 46.12%| 29.18%| 21.47%
O (Other)   | 1384  | 2.67%| 43.28%| 29.17%| 26.87%
W (White)   | 5454  | 1.72%| 29.45%| 25.39%| 43.44%

(1) Among the 14291 personnel information recorded, white people is the number one population group of being stopped by Berkeley Police. 38.16% of all records, namely 5454 people are white. black people contributes the second largest percentage. 32.44% of all records, namely 4636 people are black.

(2) The percentage of people aged from 0 to 18 of each race is less than 9%. People aged from 0 to 18 contributes the smallest percentage in each race. These teengers are looked after by their parents most of the time. 

(3) Among white people and black people recorded by the BPD, people who are over 40 are the number one group that are being stopped, which are 43.44% and 37.66% respectively.

(4) Among Asian, Hispanic and other people recorded by the BPD, people aged from 18 to 29 contribute the largest percentage, which are 43.37%, 46.12% and 43.28%, respectively.

Then we further analyzed the stop data with and without car searches by race. Since white people are the largest group to be stopped, we suspect that their possibility of car search will also be the highest. However, black people seem to be more likely to be car searched. 

### MAP: BPD All Stops w/ Car Searches by Race 2015-2016
```{r, echo=FALSE}
ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, size = CarSearch, color = Race), data = mergedf, alpha = 0.2) + 
  scale_size_discrete( "Car Search", labels = c("No Search", "Search") ) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD All Stops w/ Car Searches by Race 2015-2016") +
  facet_wrap(~ Race, ncol = 3) 
```

Even when we look at the arrest data, it is black people who are more likely to get arrest after being stopped. 

```{r, echo=FALSE}
df <- subset(mergedf, as.character(Enforcement) == "Arrest")

ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = Race), data = df, alpha = 0.5, size = 5) + 
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Stops to Arrests, by Race 2015-2016") +
  facet_wrap(~ Race) 
```


### Analysis of stop reasons 
#### Map: All stop data by reasons.
```{r, fig.height = 5, fig.width = 10, echo=FALSE}
ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = Reason), data = mergedf, alpha = 0.7, size = 3) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + ggtitle("All BPD Stops, by Reason 2015-2016") +
    facet_wrap( ~ Reason , ncol = 2)
```

From the analysis of the stop reasons, we found that the number one reason that people are stopped is traffic reason. Then we explored traffic reasons within race. As shown, black people are the highest to be stopped and arrested. 

#### Map: stop by only traffic reasons
```{r, fig.height = 5, fig.width = 10, echo=FALSE}
df <- subset(mergedf, as.character(Reason) == "Traffic")

ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = Race, size= Arrest), data = df, alpha = 0.5) + 
  scale_size_discrete( range = c(5, 2) ) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Traffic Stops Only, by Race 2015-2016") +
  facet_grid(~ Race)
```

Such contrast of being stopped, being car searched, and being arrested is further demonstrated by the arrest and jail data. 

```{r, echo=FALSE}
p1 <- ggplot(na.omit(arrest))+
  geom_bar(aes(x=Age, 
               fill = Race))+
  facet_wrap(~Race)+
 labs(x= "Age",
       y = "Number of people",
       title = "Arrest Data") 

p2 <- ggplot(na.omit(jail))+
  geom_bar(aes(x=Age,
               fill = Race))+
  facet_wrap(~Race)+
 labs(x= "Age",
       y = "Number of people",
       title = "Jail Data") 

multiplot(p1, p2,cols=2)

```

As we can clearly see from both graphs, black people are the largest group to be arrested and put into jail. 

Then we looked at the counts of people recorded of different races in every hour.Black people contribute a especially high percentage of the incidents at night, while the white people contribute a especially high percentage of the incidents at the noon.

```{r, echo=FALSE}
stop_time_percentage <- ggplot(stop_by, aes(x = Hour, fill = AgeRange)) + 
  geom_bar(aes(y = ..count..)) +
  labs(y = "Count") +
  facet_wrap(~Race)+
  labs(title = "Counts of people recorded of each race in every hour")
stop_time_percentage
```

Such analysis made us further digged into the date information. 

### Analysis of Day
```{r, echo=FALSE, eval = FALSE}
stop_day <- stop_by %>%
  ggvis(x = ~Day, fill = ~Race) %>%
  layer_bars() %>%
  add_tooltip(function(stop_by) stop_by$Race) 
  labs(title = "Counts of people recorded in every day in a week")
stop_day
```

####Picture: counts of people recorded in every day in a week
Day   | Count | A (Asian)| B (Black)| H (Hispanic) | O (Other)| W (White)
----  |------ |----------|----------|--------------|----------|------
1     | 1692  | 116      | 653      | 221          | 159      | 543
2     | 1665  | 149      | 543      | 182          | 166      | 625
3     | 2344  | 189      | 645      | 231          | 236      | 1043
4     | 2287  | 206      | 616      | 251          | 244      | 970
5     | 1941  | 152      | 592      | 223          | 168      | 806
6     | 2231  | 186      | 764      | 268          | 203      | 810
7     | 2131  | 143      | 823      | 300          | 208      | 657

(1) Among all the day in a week, the number of incidents happened on Sunday and Monday are much less than those happened through Tuesday and Saturday. 

(2) The count of records of Asian people is much less than that of any other race of people in each day and the whole week.

(3) Asian people are less liable to commit an incident on Sunday, and more liable to commit an incident on Wednesday. 

(4) Black and Hispanic people are less liable to commit an incident on Monday, and more liable to commit an incident on Saturday.

(5) White people are less liable to commit an incident on Sunday, and more liable to commit an incident on Tuesday and Wednesday, which is similar to Asian people.

## Analysis of incidents of each hour in a day
#### Picture: count of person recorded in each hour in a day
```{r, echo=FALSE}
stop_time <- stop_by %>%
  ggvis(x = ~Hour, fill := "lightpink") %>%
  layer_histograms(width = input_slider(1, 12, value = 1, step = 2, label = "width"))
stop_time
```

Note: you can change the value of the input slider to see the number of incidents happened in specific time span of the day.

#### Table: count of person recorded in each hour in a day
Hour  | Count | Hour | Count| Hour | Count| Hour | Count
----  |------ |------|------|------|------|------|------
0     | 823   | 6    | 157  | 12   | 802  | 18   | 544
1     | 618   | 7    | 341  | 13   | 695  | 19   | 685
2     | 489   | 8    | 489  | 14   | 515  | 20   | 834
3     | 289   | 9    | 582  | 15   | 542  | 21   | 971
4     | 135   | 10   | 682  | 16   | 612  | 22   | 1098
5     | 61    | 11   | 678  | 17   | 578  | 23   | 1071

(1) time span of 22:00 to 22:59 in a day has the highest incidents count, and 23:00 to 23:59 has the second highest, which means that Berkeley area is most dangerous from 10pm to 12am in a day, which corresponds to daily life experience.
(2) From 12am to 5am, incidents count decreases gradually. A reasonable conjecture of this fact is that more and more people choose to sleep as time goes by in this time span. For the similar reason, incidents count increases gradually from 5am to 11am.
(3) After the evening until the midnight, the incidents number increases gradually again in a day. The tally of the statistics and observation in daily life is in a good agreement.

#### Picture: Probability of BPD stop for a specific age range in a specific hour

```{r, echo=FALSE}
stop_by_hourCount <- stop_by %>%
  group_by(Hour) %>%
  summarise(hourcount = n())
stop_by_ageRangeCount <- stop_by %>%
  group_by(Hour, AgeRange) %>%
  summarise(ageCount = n())
stop_by_percentage <- left_join(stop_by_ageRangeCount, stop_by_hourCount, by = "Hour")
stop_by_percentage <- stop_by_percentage %>%
  mutate(percentage = ageCount/hourcount)
```

```{r, echo=FALSE}
stop_time_percentage2 <- ggplot(stop_by_percentage, aes(x = Hour, fill = AgeRange)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_wrap(~AgeRange)
stop_time_percentage2
```

(1) People aged from 18 to 29 are obviously liable to commit incidents at night. The average ratio of people aged from 18 to 29 to all people stoped by the Berkeley Police Department at night is greater than 40%.

(2) People aged greater than 40 are obviously liable to commit incidents in the daytime. The average ratio of people aged greater than 40 to all people stoped by the Berkeley Police Deparment during the day is greater than 40%.

(3) Ratio of incidents commited by people aged between 0 and 18 and people aged from 30 to 39 fluctuates during the daytime and the night, with an average ratio of 2.5% and 25% respectively.

#### Probability of BPD stop for a specific race in a specific hour

```{r, echo=FALSE}
stop_by_hourCount <- stop_by %>%
  group_by(Hour) %>%
  summarise(hourcount = n())
stop_by_raceRangeCount <- stop_by %>%
  group_by(Hour, Race) %>%
  summarise(raceCount = n())
stop_by_percentage1 <- left_join(stop_by_raceRangeCount, stop_by_hourCount, by = "Hour")
stop_by_percentage1 <- stop_by_percentage1 %>%
  mutate(percentage = raceCount/hourcount)
```
```{r, echo=FALSE}
stop_time_percentage3 <- ggplot(stop_by_percentage1, aes(x = Hour, fill = Race)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_wrap(~Race)
stop_time_percentage3
```

(1) Black people are obviously liable to commit incidents at night. The average ratio of black people to all people stoped by the Berkeley Police Department at night is about 40%.

(2) White people are obviously liable to commit incidents in the daytime. The average ratio of white people to all people stoped by the Berkeley Police Deparment during the day is about 45%.

(3) Ratio of incidents commited by Asian people, Hispanic people and other people fluctuate during the daytime and the night, with an average ratio of 8%, 11% and 9% respectively.


### Analysis of preference of Berkeley Police Department arresting people
#### Picture: Probability of arrested by BPD of a specific race for a specific reason
```{r,echo=FALSE}
stop_by_reason_race <- stop_by %>%
  group_by(Race, Reason) %>%
  summarise(totalCount = n())
stop_by_arrest <- stop_by %>%
  filter(Enforcement == "A") %>%
  group_by(Race, Reason) %>%
  summarise(arrestCount = n())
stop_by_percentage_race <- left_join(stop_by_reason_race, stop_by_arrest, by = c("Race", "Reason"))
stop_by_percentage_race <- stop_by_percentage_race %>%
  mutate(percentage = arrestCount / totalCount)
stop_arrest <- ggplot(stop_by_percentage_race, aes(x = Race, fill = Race)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_wrap(~Reason)
stop_arrest
```

#### Table: Probability of arrested by BPD of a specific race for a specific reason
P   | I      | K     | R     | T     | W     |
----|------- |-------|-------|-------|-------|
A   | 10.34% | 75%   | 10.34%| 1.24% | 17.60%|
B   | 8.31%  | 15.79%| 6.44% | 2.28% | 50.00%|  
H   | 6.98%  | 16.67%| 9.09% | 2.90% | 25.00%| 
O   | 10.14% | 18.18%| 5.80% | 0.41% | 41.67%| 
W   | 8.14%  | 26.79%| 3.40% | 1.04% | 32.56%| 

Note: in the picture and table above, I for Investigation, T for Traffic, R for Reasonable Suspicion, K for Probation/Parole, W for wanted.

(1) The probability of arrested in a stop with the reason Traffic is much lower than other reasons. The average conditional probability of arrested given reason is traffic is 1.58%.

(2) The probability of arrested in a stop with the reason Wanted is much higher than other reason. The average conditional probability of arrested given reason is wanted is 33.33%.

(3) An interesting fact is that the conditional probability of arrested in a stop with the reason Probation or Parole and race Asian is 75%, which is much higher than that of any other race. Asian people is much more liable to be arrested by Berkeley Police Department during Probation or Parole if stopped by the BPD.

#### Picture: Probability of arrested by BPD of a specific age range for a specific reason
```{r, echo=FALSE}
stop_by_reason_age <- stop_by %>%
  group_by(AgeRange, Reason) %>%
  summarise(totalCount = n())
stop_by_arrest_age <- stop_by %>%
  filter(Enforcement == "A") %>%
  group_by(AgeRange, Reason) %>%
  summarise(arrestCount = n())
stop_by_percentage_age <- left_join(stop_by_reason_age, stop_by_arrest_age, by = c("AgeRange", "Reason"))
stop_by_percentage_age <- stop_by_percentage_age %>%
  mutate(percentage = arrestCount / totalCount)

stop_arrest_age <- ggplot(stop_by_percentage_age, aes(x = AgeRange, fill = AgeRange)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_wrap(~Reason)
stop_arrest_age
```

#### Table: Probability of arrested by BPD of a specific age range for a specific reason
P     | I (Investigation) |K (Probation/ Parole)| R (Reasonable Suspicion)|T (Traffic)| W (Wanted) 
----  |------------------ |---------------------|-------------------------|-----------|-------
0-18  | 17.95%            | 67.57%              | 13.95%                  | 3.24%     | 50.00%  
18-29 | 8.45%             | 12.50%              | 3.87%                   | 1.82%     | 32.35%  
30-39 | 6.32%             | 25.00%              | 5.04%                   | 1.49%     | 26.92%  
40+   | 7.87%             | 23.86%              | 6.13%                   | 1.41%     | 31.82%  

(1) Similar to the conclusions above, the probability of arrested in a stop with the reason Traffic is the lowest and wanted is the highest.

(2) Again similar to the conclusion above, an interesting fact is that the conditional probability of arrested in a stop with the reason Probation or Parole and age range 0-18 is 67.56%, which is much higher than that of any other age range.

(3) The conditional probability of arrested given person involved aged from 0 to 18 in a stop given any reason is more than that of given person with any other age range. Therefore, in a stop, teenagers is more liable to be arrested by Berkeley Police Department.

#### Picture: Probability of arrested by BPD of a specific gender for a specific reason
```{r, echo=FALSE}
stop_by_reason_gender <- stop_by %>%
  group_by(Gender, Reason) %>%
  summarise(totalCount = n())
stop_by_arrest_gender <- stop_by %>%
  filter(Enforcement == "A") %>%
  group_by(Gender, Reason) %>%
  summarise(arrestCount = n())
stop_by_percentage_gender <- left_join(stop_by_reason_gender, stop_by_arrest_gender, by = c("Gender", "Reason"))
stop_by_percentage_gender <- stop_by_percentage_gender %>%
  mutate(percentage = arrestCount / totalCount)

stop_arrest_gender <- ggplot(stop_by_percentage_gender, aes(x = Gender, fill = Gender)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_wrap(~Reason)
stop_arrest_gender
```

#### Table: Probability of arrested by BPD of a specific gender range for a specific reason
P     | I (Investigation) |K (Probation/ Parole)| R (Reasonable Suspicion)|T (Traffic)| W (Wanted) 
----  |------------------ |---------------------|-------------------------|-----------|-------
F     | 9.05%             | 50.00%              | 5.00%                   | 1.10%     | 28.57%  
M     | 8.26%             | 20.11%              | 5.42%                   | 1.85%     | 37.04%  

(1) Similar to the conclusions above, the probability of arrested in a stop with the reason Traffic is the lowest and wanted is the highest.

(2) Again similar to the conclusion above, an interesting fact is that the conditional probability of arrested in a stop with the reason Probation or Parole of female is 50.00%, which is much higher than that of male, which is 20.11%.



## Conclusion

1. From analyzing the relationship between population density and stop data density, we found that he place that are the most likely to be stopped is not the place where most people live, but the transportation hub.
2. From various analysis of the data by race, such as the stop time by race, car search by race, we found that black people are the number one to be arrested and even put into jail. Surprisingly, they are not the number one to be stopped. White people are the largest group to be stopped. 
3. During daytime, young people and white people are more likely to be stopped. During nightime, people over 40 and black people are more likely to be stopped by police. 
4. Asian and female are more likely to be arrested by the BDP for probation/parole. 








```{r}

  
  theme(axis.line = element_line(size=1, colour = "black"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.border = element_blank(), 
        panel.background = element_blank())


  theme(plot.title=element_text(family="xkcd-Regular"), 
        text=element_text(family="xkcd-Regular"), 
        axis.text.x=element_text(colour="black", size = 10), 
        axis.text.y=element_text(colour="black", size = 10)) 



p1 <- ggplot(mergedf)+
  geom_bar(aes(x=Race),
           fill = c("#FFCC00","#E1B378","#5F9EA0","#66FFCC","#40B8D0"))+
  labs(title = "Stop data by race",
       x = "Race",
       y = "Counts")

p2 <- ggplot(race)+
  geom_bar(aes(x=Race, 
               y=census),
           stat = "identity", 
           fill = c("#FFCC00","#E1B378","#5F9EA0","#66FFCC","#40B8D0"))+
  labs(title = "Demographic race data",
       x = "Race",
       y = "Counts")

multiplot(p1, p2,cols=2)


c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF")


ggplot(mtcars, aes(factor(cyl))) + 
          geom_bar(aes(y = (..count..)/sum(..count..))) + 
          scale_y_continuous(labels=percent)

c("#FFCC00","#E1B378","#5F9EA0","#66FFCC","#40B8D0")


ggplot(pop)+
  geom_bar(aes(x=Race,
               y=(stop/census)), 
           stat = "identity",
           fill = c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF"))+
  geom_text(aes(x = Race, 
                y = (stop/census), 
                label = paste0((stop/census),"%")), 
            size=3)+
  scale_y_continuous(labels=percent)+
  labs(title = "The percentage of being stopped by police",
       x = "Race",
       y = "Percentage")


```



```{r}
############################## stop data ############################## 
stop_by <- read_csv("cleaned_stop_data.csv")

stop_by$Call.Date.Time <- mdy_hm(stop_by$Call.Date.Time)
stop_by$AgeRange <- as.factor(stop_by$AgeRange)

stop_by <- stop_by %>%
  mutate(Hour = as.integer(hour(Call.Date.Time))) %>%
  mutate(Day = as.factor(as.integer(wday(Call.Date.Time))))

stop_by$Race<- stop_by$Race %>% 
  str_replace("A", "Asian") %>% 
  str_replace("B", "Black") %>% 
  str_replace("H", "Hispanic") %>% 
  str_replace("O", "Other") %>% 
  str_replace("W", "White")

stop_by$Gender<- stop_by$Gender %>% 
  str_replace("F", "Female") %>% 
  str_replace("M", "Male") 

stop_by$Reason <- stop_by$Reason %>% 
  str_replace("I", "Investigation") %>% 
  str_replace("T", "Traffic") %>% 
  str_replace("R", "Reasonable Suspicion") %>% 
  str_replace("R", "Probation/ Parole") %>% 
  str_replace("W", "Wanted")

stop_by$Enforcement <- stop_by$Enforcement %>% 
  str_replace("A", "Arrest") %>% 
  str_replace("C", "Citation") %>% 
  str_replace("O", "Other") %>% 
  str_replace("W", "Warning")

stop_by$CarSearch <- stop_by$CarSearch %>% 
  str_replace("S", "Search") %>% 
  str_replace("N", "No Search")
```



```{r}


```{r}
race %>%
  ggvis(x = ~Description, y = ~Counts) %>%
  layer_bars(fill = c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF")) %>%
  add_tooltip(function(race) race$Counts) 
  labs(title = "Counts of people recorded in every day in a week")


```

```






