---
title: "Arrest and Jail Bookings"
author: "Shangjun Jiang"
date: "22 July 2016"
output: html_document
---

```{r}
setwd("~/Desktop/Stats R/PROJECT/finalproject_angry_ladies/Jenny_Analysis")
```

#load packages
```{r}
library(xml2)
library(rvest)
library(ggplot2)
library(lubridate)
library(stringr)
library(dplyr)
library(tidyr)
library(readr)
library(shiny)
library(ggvis)
```


#load datasets
```{r}
jail <- read.csv("Berkeley_PD_Log_-_Jail_Bookings.csv")
jail$Age <- as.integer(jail$Age)
jail$Age[jail$Age<20] <- "0-19"
jail$Age[jail$Age>=20 & jail$Age<30] <- "20-29"
jail$Age[jail$Age>=30 & jail$Age<40] <- "30-39"
jail$Age[jail$Age>=40 & jail$Age<50] <- "40-49"
jail$Age[jail$Age>=50 & jail$Age<60] <- "50-59"
jail$Age[jail$Age>=60 & jail$Age<70] <- "60-69"
jail$Age[jail$Age>=70 & jail$Age<80] <- "70-79"
jail$Age <- as.factor(jail$Age)



arrest <- read.csv("Berkeley_PD_Log_-_Arrests.csv")
arrest$Age <- as.integer(arrest$Age)
arrest$Age[arrest$Age<20] <- "0-19"
arrest$Age[arrest$Age>=20 & arrest$Age<30] <- "20-29"
arrest$Age[arrest$Age>=30 & arrest$Age<40] <- "30-39"
arrest$Age[arrest$Age>=40 & arrest$Age<50] <- "40-49"
arrest$Age[arrest$Age>=50 & arrest$Age<60] <- "50-59"
arrest$Age[arrest$Age>=60 & arrest$Age<70] <- "60-69"
arrest$Age[arrest$Age>=70 & arrest$Age<80] <- "70-79"
arrest$Age <- as.factor(arrest$Age)
       
jail[jail == ""] <- NA

arrest[arrest == ""] <- NA

#str(jail) # 'data.frame':	249 obs. of  19 variables:

#str(arrest) # 232 obs. of  16 variables:
```

# differences between jail and arreasts   match 28/29  
# delete status desription
# subject, race, age, height, weight, hair, eyes, status, status.type, status.description, case.number


#graph the race data  1. Black 2. White 
# status. type 
#graph the age data 

```{r}
## Disposition 

length(which(jail$Disposition == "NO COMPLAINT"))   #28
length(jail[which(jail$Disposition == "NO COMPLAINT"),]) #19
jail[which(jail$Disposition == "NO COMPLAINT"),]

jail[jail$Disposition == "BAILED",]  #19

length(which(jail$Disposition == "BAILED"))  #14

length(jail[jail$Disposition == "CITE-JAIL",])  #19

#SANTA RITA JAIL
length(jail[jail$Disposition == "SANTA RITA JAIL",])  #19

length(jail[jail$Disposition == "849(b) PC-RELEASEL",])  #19

jail$Disposition == "849(b) PC-RELEASEL"



```

#clean jail dataset and arrest dataset in order to combine them together
```{r}

cleanedjail <- jail
cleanedjail$Statute <- NULL
cleanedjail$Statute.Description <- NULL
cleanedjail$Height <- NULL
cleanedjail$Weight <- NULL
cleanedjail$Hair <- NULL
cleanedjail$Eyes <- NULL
cleanedjail$Date.Of.Birth <- NULL
cleanedjail$Subject <- tolower(cleanedjail$Subject)
names(cleanedjail) <- c("Booking_Number","Booking_Date_Time", "Subject", "Race", "Sex","Age", "Occupation","Statute_Type", "Arrest_Date_Time","Case_Number","Booking_Agency", "Disposition")

cleanedarrest <- arrest
cleanedarrest$Statute <- NULL
cleanedarrest$Statute.Description <- NULL
cleanedarrest$Height <- NULL
cleanedarrest$Weight <- NULL
cleanedarrest$Hair <- NULL
cleanedarrest$Eyes <- NULL
cleanedarrest$Date.of.Birth <- NULL
cleanedarrest$Subject <- tolower(cleanedarrest$Subject)
names(cleanedarrest) <- c("Arrest_Number", "Date_Time", "Arrest_Type", "Subject", "Race", "Sex", "Age", "Statute_Type", "Case_Number")

names(cleanedarrest)
names(cleanedjail)

comb <- inner_join(cleanedarrest,cleanedjail, by=c("Case_Number", "Race", "Sex", "Age", "Subject", "Statute_Type"))
names(comb)

#join two lists together
ja <- inner_join(arrest,jail, by="Case.Number")
left_join
str(ja) #'data.frame':	28 obs. of  23 variables:

```


```{r}
ggplot(cleanedjail)+
  geom_bar(aes(x=Booking_Agency))

#CA0010300 Berkeley Police Department
#CA0019700 UC Berkeley Police Department

```

# Disposition
```{r}
ggplot(jail)+
  geom_bar(aes(x=Disposition))

```



#people who are in jail
```{r}

ggplot(na.omit(jail))+
  geom_bar(aes(x=Age, 
               fill = Race))+
  facet_wrap(~Sex)+
  labs(x= "Age",
       y = "Number of people",
       title = "Jail Data")


ggplot(na.omit(jail))+
  geom_bar(aes(x=Occupation, 
               fill=Race))


```




## Arrest dataset


```{r,fig.width=10, fig.asp=0.7}
ggplot(na.omit(arrest))+
  geom_bar(aes(x=Age, fill = Sex))+
  facet_wrap(~Race)+
 labs(x= "Age",
       y = "Number of people",
       title = "Arrest Data")
```


#people who are arrest
```{r}
ggplot(na.omit(arrest))+
  geom_bar(aes(x=Age, fill = Sex))+
  facet_wrap(~Race)+
 labs(x= "Age",
       y = "Number of people",
       title = "Arrest Data")



ggplot(na.omit(arrest))+
  geom_bar(aes(x=Age, fill = Race))+
  facet_wrap(~Sex)

arrest$Age <- as.factor(arrest$Age)


ggplot(na.omit(arrest))+
  geom_bar(aes(x=Race, fill=Age))+
  facet_wrap(~Sex)

```

#occupation
```{r}
ggplot(na.omit(jail))+
  geom_bar(aes(x=Occupation))



```











