---
title: "wk5"
author: "Shangjun Jiang"
date: "29 June 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(lubridate)
library(ggplot2)
library(ggrepel)

```


## Read in the data
```{r}
setwd("~/Desktop/Stats R/stat133-su2016/14-lesson/")
corrupt <- read.csv("EconomistData.csv")
str(corrupt)

```


## Make a basic plot
```{r}
ggplot(corrupt,aes(x=CPI,y=HDI))+geom_point(aes(color=Region))

```

## second layer+aesthetics
```{r}
ggplot(corrupt,aes(x=CPI,y=HDI))+geom_smooth(method="lm",formula=y~log(x),se=FALSE,color="red")+geom_point(aes(color=Region),shape=1,size=2,stroke=1.5)

```

## adding the text
```{r}
points_to_label <- c("Russia", "Venezuela", "Iraq", "Myanmar", "Sudan",
                     "Afghanistan", "Congo", "Greece", "Argentina", "Brazil",
                     "India", "Italy", "China", "South Africa", "Spane",
                     "Botswana", "Cape Verde", "Bhutan", "Rwanda", "France",
                     "United States", "Germany", "Britain", "Barbados", "Norway", 
                     "Japan", "New Zealand", "Singapore")

length(points_to_label)
cc<- filter(corrupt, Country%in%points_to_label)
cc
length(cc)

str(corrupt$Country)

?geom_text

ggplot(corrupt,aes(x=CPI,y=HDI))+
  geom_smooth(method="lm",formula=y~log(x),se=FALSE,color="red")+
    geom_point(aes(color=Region),shape=1,size=2,stroke=1.5)+ 
      geom_text_repel(data=cc,aes(label =Country), colour="gray20")
```

## modifying the legend
The legend names are off. Use mutate and factor to change the label of the levels of Region. Reason your way through the equialencies if you’re not familiar.
```{r}
mc<- mutate(corrupt, Region=
         str_replace(corrupt$Region, "EU W. Europe", "OECD") %>% 
        str_replace("Asia Pacific", "Asia&Oceania") %>% 
       str_replace("East EU Cemt Asia", "Central&Eastern Europe") %>% 
       str_replace("MENA", "Middle East & north Africa") %>% 
       str_replace("SSA", "Sub-Saharan Africa"))


ggplot(mc,aes(x=CPI,y=HDI))+
  geom_smooth(method="lm",formula=y~log(x),se=FALSE,color="red")+
    geom_point(aes(color=Region),shape=1,size=2,stroke=1.5)+ 
      geom_text_repel(data=cc,aes(label =Country), colour="gray20")

```

OECD  <- EU W. Europe
Americas  <- Americas
Asia&Oceania <- Asia Pacific
Central&Eastern Europe <- East EU Cemt Asia
Middle East & north Africa  <- MENA
Sub-Saharan Africa  <-SSA

## Adding the titles
```{r}

ggplot(mc,aes(x=CPI,y=HDI))+
  geom_smooth(method="lm",formula=y~log(x),se=FALSE,color="red")+
    geom_point(aes(color=Region),shape=1,size=2,stroke=1.5)+ 
      geom_text_repel(data=cc,aes(label =Country), colour="gray20")+
  labs(title="Corruption and Human development", x="Corruption Perceptions Index, 2011 (10=least corrupt)", y = "Human Development Index, 2011 (1=Best)", fill = "Region")


```

## modifying the scales
```{r, fig.width = 9, fig.asp = .5}

ggplot(mc,aes(x=CPI,y=HDI))+
  geom_smooth(method="lm",formula=y~log(x),se=FALSE,color="red")+
  geom_point(aes(color=Region),shape=1,size=2,stroke=1.5)+ 
  geom_text_repel(data=cc,aes(label =Country), colour="gray20")+
  labs(title="Corruption and Human development", x="Corruption Perceptions Index, 2011 (10=least corrupt)", y = "Human Development Index, 2011 (1=Best)", fill = "Region")+
  scale_x_continuous(limits=c(1,10),breaks=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(limits=c(0.2,1.0), breaks = c(0.2,0.4,0.6,0.8,1.0))+
  scale_color_manual(values=c("#099DD7", "#248E84", "#28AADC", "#24576D", "#96503F", "#F2583F" ))+
  theme_minimal()





```



```{r, eval = F}
text = element_text(color = "gray20"),
legend.justification = 0.1, # anchor point for legend.position.
legend.text = element_text(size = 11, color = "gray10"),
axis.text = element_text(face = "italic"),
axis.title.x = element_text(vjust = -1), # move title away from axis
axis.title.y = element_text(vjust = 2), # move away for axis
axis.line = element_line(color = "gray40", size = 0.5),
panel.grid.major = element_line(color = "gray50", size = 0.5),
panel.grid.major.x = element_blank()
```


```{r,eval = F}
footnote <- "Sources: Transparency International; UN Human Development Report"
footgrob <- textGrob(footnote, x = 0, hjust = -0.1, vjust=0.1, gp = gpar(fontface = "italic", fontsize = 12))
g <- arrangeGrob(p, bottom = footgrob)
grid.draw(g)
```
































