---
title: "HW6"
author: "Shangjun Jiang"
date: "18 July 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("~/Desktop/Stats R/githubrepos-jennyjiang95/hw6/ggvis")
```



```{r, eval = FALSE}
rsconnect::setAccountInfo(name='shangjunjiang', token='D7F4094AA60A38ED55C859BCC4B89760', secret='hNkCcBfLkzNZUac6mbVuSH6DD2GD3owqEcksI5+9')
rsconnect::setAccountInfo(name='shangjunjiang', token='D7F4094AA60A38ED55C859BCC4B89760', secret='hNkCcBfLkzNZUac6mbVuSH6DD2GD3owqEcksI5+9')

library(rsconnect)
rsconnect::deployApp("~/Desktop/Stats R/githubrepos-jennyjiang95/hw6/ggvis")

rsconnect::deployApp("~/Desktop/Stats R/githubrepos-jennyjiang95/hw7/wordchoice")

library(shiny)
runApp()
library(rsconnect)
deployApp()

rsconnect::deployApp("~/Desktop/Stats R/githubrepos-jennyjiang95/hw6")
 
```




```{r}
select(df, FirstVar)
select_(df, .dots = list("FirstVar"))
?filter_
str(cleaned)
filter_criteria <- ~ "What word(s) do you use to address a group of two or more people?" %in% cleaned$quest
cleaned %>% 
  filter_(.dots = filter_criteria) %>% 
  collect()

cleaned$quest
cleaned1 <- cleaned %>% 
  filter(quest == "What do you say when you want to lay claim to the front seat of a car?")
 
str(comb)
tail(comb)
head(comb)
comb$ans
comb$qnum
question$quest
data
comb$quest[3170557]

str(data)
names(statemax)
statemax$quest
scale_t

cleaned1
ggplot(cleaned1) + 
      geom_polygon(aes_string(x = "long", y = "lat", fill = "ans", group = "group"), 
                   color = "black") + 
      coord_fixed(1.3)

filter_(cleaned, 
        list("quest") == "What word(s) do you use to address a group of two or more people?", 
        .dots)

cleaned %>% 
  filter(quest =="What word(s) do you use to address a group of two or more people?")
  filter_(cleaned, 
          list("quest") == "What word(s) do you use to address a group of two or more people?", 
          .dots)

```



```{r}

rsconnect::deployApp("~/Desktop/Stats R/githubrepos-jennyjiang95/hw7/usa")
#graph
```{r}
names(cleaned) <-c ("number","long","lat","group","order","region","subregion","quest","ans","n")
cleaned
cleaned1 <- cleaned %>% 
  filter(quest == "What word(s) do you use to address a group of two or more people?")
ggplot(cleaned1) + 
  geom_polygon(aes(x = long, y = lat, fill = ans, group = group), color = "black") + 
  coord_fixed(1.3)

rsconnect::deployApp("~/Desktop/Stats R/githubrepos-jennyjiang95/hw7")
rsconnect::deployApp("~/Desktop/Stats R/githubrepos-jennyjiang95/hw7/usa")

runApp()
deployApp("~/Desktop/Stats R/githubrepos-jennyjiang95/hw7/usa")

```

```



```{r}
library(xml2)
library(rvest)
library(ggplot2)
library(lubridate)
library(stringr)
library(dplyr)
library(tidyr)
library(readr)
library(shiny)
```


# cleaned_demographics.csv 
```{r}
#read the google sheet
region <- read_html("https://docs.google.com/spreadsheets/d/1OxmGUNWeADbPJkQxVPupSOK5MbAECdqThnvyPrwG5Os/pub?gid=1#") %>% 
  html_nodes(xpath= "//*[@class='waffle']") %>%
  .[[2]] %>% 
  html_table(fill = TRUE)
names(region) <- c("No","Country", "Group", "ID")

# read files
gdp <- read.csv("gdppc.csv")
pop<- read.csv("population.csv")
life <- read.csv("lifeexpectancy.csv")

#clean the data
pop$NA. <- NULL
pop$NA..1 <- NULL
pop$NA..2 <- NULL
pop$NA..3 <- NULL
pop$NA..4 <- NULL
pop$NA..5 <- NULL
pop$NA..6 <- NULL
pop$NA..7 <- NULL
pop$NA..8 <- NULL
pop$NA..9 <- NULL

#change the year date
names(gdp) <- str_replace(names(gdp),"^X", "") %>%   #217
  str_replace(".0$", "")
names(pop) <- str_replace(names(pop),"^X", "") %>%   #82 . 92
  str_replace(".0$", "")
names(life)<- str_replace(names(life),"^X", "") %>%    #217
  str_replace(".0$", "")


#filter the na in country
pop <- filter(pop, !is.na(pop$Total.population))
gdp <- filter(gdp, !is.na(gdp$GDP.per.capita))
life <-filter(life,!is.na(life$Life.expectancy.with.projections..Yellow.is.IHME))

#gdp
ggdp <- gather(gdp, key=year, value = GDP.per.capita)
names(ggdp) <- c("Country", "Year", "GDP per capita")
ggdp$Year<- as.integer(ggdp$Year)
#ggdp <- ggdp[complete.cases(ggdp[,1]),]  #56160

#life
llife <- gather(life, key=year, value = Life.expectancy.with.projections..Yellow.is.IHME)
names(llife) <- c("Country", "Year", "Life Expectancy")
llife$Year<- as.integer(llife$Year)
#llife <- llife[complete.cases(llife[,1]),]  #56160

#population
ppop <- gather(pop, key=year, value = Total.population, -1)
names(ppop) <- c("Country", "Year", "Total Population")   #56420
ppop$Year<- as.integer(ppop$Year)

#find the missing year
yyear <- setdiff(min(ppop$Year):max(ppop$Year),unique(ppop$Year))
#unique country
ccountry <- unique(ppop$Country)

#new data frame missing year and country and population
nyear <- lapply(yyear,function(x){
  data.frame(Country = ccountry, Year= rep(x,275), Population = NA)
})

#make it into one dataframe
myear <- do.call(rbind,nyear)
names(myear) <- c("Country","Year","Total Population")

#merge two data frames together
ppop <- rbind(ppop,myear)

#create a decade 
ppop$Year <- as.integer(ppop$Year)
ppop <- mutate(ppop, decade = ((Year%/%10) *10))

#group by decade and country and get mean 
ppop<- ppop %>% 
  group_by(decade, Country) %>% 
  mutate(mean(`Total Population`, na.rm= T)) %>% 
  arrange(Year)

#delete the NOT useful column
names(ppop) <- c("Country", "Year", "TP", "Decade", "Total Population")
ppop$Decade <- NULL
ppop$TP <- NULL


# only leave the group and the country. 
region$No <- NULL
region$ID <- NULL
# delete the names on the first row
region <- region[-1,]

###join the three data frame together
#join gdp and life 
gl <- full_join(ggdp,llife, by = c("Country", "Year"))
gp <- inner_join(gl,ppop, by= c("Country", "Year"))
sum <- inner_join(gp,region, by = "Country")

#as factor
sum$Country <- as.factor(sum$Country)
sum$Year <- as.factor(sum$Year)
sum$Group <- as.factor(sum$Group)

write.csv(sum,"cleaned_demographics.csv")

###join the three data frame together

?scale_size_gradient
scale_size_manual()

min(sum$`Total Population`, na.rm = T)
max(sum$`Total Population`, na.rm = T)

scale_size_manual(limits = c(50, 1358754840))
?scale_size
breaks
labels
limits = c(50, 1358754840)
trans= "log10"

,
                 breaks = seq(50, 1358754840, by = 20000),
                 trans= "log10")


str(ggdp)
str(llife)
str(ppop)

class(ppop)
names(ppop)
str(gl)
str(gp)
str(gr)
str(sum)

#join gdp with the region
gr <- inner_join(ggdp,region,by = "Country")

full_join(gr,llife,by = "Country", "Year")

str(gr)
str(llife)

gl<- full_join(ggdp, llife)
glp <- full_join(gl, ppop)
# only leave the group and the country. 
region$No <- NULL
region$ID <- NULL

sum <- full_join(glp,region, by = "Country")

#as factor
sum$Country <- as.factor(sum$Country)
sum$Year <- as.factor(sum$Year)
sum$Group <- as.factor(sum$Group)

write.csv(sum,"cleaned_demographics.csv")

str(glp)
str(region)
str(sum)


str(ggdp)

a <- data.frame(sum$Country, sum$`GDP per capita`)

----------------------------------------------------------------------------

  ggplot(na.omit(ggdp)) +
  geom_bar(aes (x= "GDP per capita"), na.rm=T)

  
ggplot(na.omit(sum)) +
  geom_point(aes(x="Year", y = "Life Expectancy"), na.rm=T)
  
  
ggplot(sum,aes(x,y = value, color = variable)) +
  geom_point(aes(x="Year", y = "Life Expectancy", color = "Group"), na.rm=T)
  
geom_point()
arra

unique(ppop$Year)

1801 %/% 10
(ppop$Year%/%10)*10
#1800-1810; 1940-1949

intersect(min(ppop$Year):max(ppop$Year),unique(ppop$Year))

for (i in (1800: 1950)) {
  for (ppop$Year== i) {
    str_replace(nyear, NA, ppop %>% 
                  group_by(Country) %>% 
                  summarise(mean(`Total Population`, na.rm= T)))
  }
}

#create a decade 
ppp <- ppop %>% 
  subset(Year <"1951") %>% 
  group_by(Country, Year) %>% 
  summarise(mean(`Total Population`, na.rm= T))

rep(1:nrow(ppp), ppp[, 2])

rep( 1:nrow(x) , x[ , 2 ] )

if myear$Year

mutate(ppop, decade = decade)
syear <- subset(ppop, ppop$Year < "1951") 
decade <- str_match(syear$Year,".*0$")

decade

for (ppop$Year < "1951"){
  str_extract(sp$Year, ".*0$")
}

syear <- subset(ppop, ppop$Year < "1951") 
str_extract(syear$Year,".*0$")


ppop$Year[str_extract(ppop$Year, ".*0$"), na.rm= T]


ppp <- ppop %>% 
  subset(Year <"1951") %>% 
  group_by(Country, Year) %>% 
  summarise(mean(`Total Population`, na.rm= T))




ppop %>% 
  group_by(Country) %>% 
  summarise(mean(`Total Population`, na.rm= T))

ppop %>% 
  group_by(Year)


ccountry 

if nyear$Country == 

  
str(ppop)
group_by(ppop, ppop$Year)


#ppop <- ppop[complete.cases(ppop[,1]),]   #25025

#combine gdp and life expectancy
bb <- inner_join(ggdp, llife)
bb$Year <- as.factor(bb$Year)




#add population in
total <- inner_join(bb,ppop, by = "Country")

write.csv(total, "total.csv")

total$Country <- as.factor(total$Country)
#add region in
sum <- inner_join(region,total, by= "Country")

#as.factor(sum$Year)

#write.csv(sum,"cleaned_demographics.csv")

#str(bb)
```


```{r}
na.omit(subset(graph, Year== selected_year)) %>% 
      ggvis (x = ~"GDP_per_capita", 
             y = ~"Life_Expectancy"
             
```

## Questions:
1. Q1: trim white space 
4. Q2: graph. how? geom_point? 


guides(size= FALSE, alphoa = FALSE)

```{r}

sp, rgdal, and rgeos, 


library(maps)
library(mapdata)
usa <- map_data("usa")
ggplot() + 
  geom_polygon(data = usa, aes(x=long, y = lat, group = group)) + 
  coord_fixed(1.3)

states <- map_data("state")
ggplot(states) + 
  geom_polygon(aes(x = long, y = lat, fill = region, group = group), color = "white") + 
  coord_fixed(1.3) +
  guides(fill = FALSE) 


setdiff(min(pop$Year),max(pop$Year),unique(pop$Year))
str(ppop)

setdiff(pop,gdp)
str(gdp)
str(pop)
is.element(pop,gdp)  # 92
is.element(gdp,pop)  #217
intersect(gdp,pop)
setequal( union(x, y),
          c(setdiff(x, y), intersect(x, y), setdiff(y, x)))

```
mutate(pop, c(X1801.0,X1802.0) = X1800.0)
?mutate_

# Column-based approach: make use of the recycling rule and mutate_ along with setdiff
 
# Row-based approach: Somehow use gather, summarise, and a join to fill in the gaps.

18


```{r}
#population data missing 1800-1810; 1940-1949
str(pop)
pop <- mutate(pop, X1801.0 = X1800.0)
pop <- mutate(pop, X1802.0 = X1800.0)
pop <- mutate(pop, X1803.0 = X1800.0)
pop <- mutate(pop, X1804.0 = X1800.0)
pop <- mutate(pop, X1805.0 = X1800.0)
pop <- mutate(pop, X1806.0 = X1810.0)
pop <- mutate(pop, X1807.0 = X1810.0)
pop <- mutate(pop, X1808.0 = X1810.0)
pop <- mutate(pop, X1809.0 = X1810.0)
pop <- mutate(pop, X1811.0 = X1810.0)
pop <- mutate(pop, X1812.0 = X1810.0)
pop <- mutate(pop, X1813.0 = X1810.0)
pop <- mutate(pop, X1814.0 = X1810.0)
pop <- mutate(pop, X1815.0 = X1810.0)
pop <- mutate(pop, X1816.0 = X1820.0)
pop <- mutate(pop, X1817.0 = X1820.0)
pop <- mutate(pop, X1818.0 = X1820.0)
pop <- mutate(pop, X1819.0 = X1820.0)
pop <- mutate(pop, X1821.0 = X1820.0)
pop <- mutate(pop, X1822.0 = X1820.0)
pop <- mutate(pop, X1823.0 = X1820.0)
pop <- mutate(pop, X1824.0 = X1820.0)
pop <- mutate(pop, X1825.0 = X1820.0)
pop <- mutate(pop, X1826.0 = X1830.0)
pop <- mutate(pop, X1827.0 = X1830.0)
pop <- mutate(pop, X1828.0 = X1830.0)
pop <- mutate(pop, X1829.0 = X1830.0)
pop <- mutate(pop, X1841.0 = X1830.0)

a <- 
?setdiff

str(pop)

class(pop$X1800.0)

setdiff(min(ppop$year),max(ppop$year),unique(ppop$year))


```


```{r}
ggplot(bb, aes(x="GDP per capita", y = "Life Expectancy")) +
  geom_point(na.rm=T)

ggplot(sum,aes(x="GDP per capita", y = "Life Expectancy")) +
  geom_point(na.rm=T)

ggplot(na.omit(sum))+
  geom_point(aes(x = "Year", y = "Life Expectancy"))

ggplot(subset(sum, Year = "1800"))+
   geom_point(aes(x="GDP per capita", y = "Life Expectancy"), na.rm = T)

a <- subset(sum, Year == "1800")
str(na)
class(a)
str(a)
na <- na.omit(a)
na$`GDP per capita`

str(sum)
max(sum$`GDP per capita`,na.rm = T)  #182668

  +
  scale_x_continuous(limits = c(500, 182668),
                     breaks = seq(500,182668, by = 91084)) +
  scale_y_continuous(limits = c(25,75),
                     breaks = seq(25,75, by = 25),
                     labels=c("25" = "25 \nyears", 
                              "50" = "50 \nyears",
                              "75" = "75 \nyears")) +
    labs(title = "Year",
         x = "GDP Per Capita (Inflation-Adjusted)",
         y = "Life Expectancy Birth")

#,
                   #shape = 21),


scale_x_continuous(labels = dollar_format(prefix = "$")


      scale_size(limits = c(50, 1358754840),
                 trans= "log10") +


ggplot(na.omit(subset(sum, Year=="1900"))) + 
    geom_point(aes(x = `GDP per capita`, 
                   y = `Life Expectancy`, 
                   color = Group,
                   size = `Total Population`),
               na.rm=T) +
  guides (size = FALSE, alpha = FALSE)
  scale_x_continuous(limits = c(500, max(sum$`GDP per capita`,na.rm = T)),
                     breaks = seq(500,max(sum$`GDP per capita`,na.rm = T), by = (max(sum$`GDP per capita`,na.rm = T)-500)/2),
                     labels = c ("500" ="$500",
                                 "90000" = "$5000",
                                 "91084" ="$50000")) +
  scale_y_continuous(limits = c(25,75),
                     breaks = seq(25,75, by = 25),
                     labels=c("25" = "25 \nyears", 
                              "50" = "50 \nyears",
                              "75" = "75 \nyears")) +
    labs(title = "Year",
         x = "GDP Per Capita (Inflation-Adjusted)",
         y = "Life Expectancy Birth")
  

?scale_x_manual
?scale_y_discrete

labels=c("0.5" = "Dose 0.5", "1" = "Dose 1",
                              "2" = "Dose 2")


?ggplot
?geom_point

ggplot(na.omit(a))+
  geom_point(aes(x="GDP per capita", y = "Country", fill = "Group"), na.rm = T)


?geom_dotplot

ggplot(data[which(data$`Reactor Type` != ""),])+
  geom_point(aes(x=year(const_start),
                 y=net, 
                 shape = `Reactor Type`, 
                 color = Country),
             size = 2)

```



#rename
names(gdp)[names(gdp)=="GDP.per.capita"] <- "Country"
names(pop)[names(pop)=="total.population"] <- "Country"
names(life)[names(life)=="Life.expectancy.with.projections..Yellow.is.IHME"] <- "Country"



```{r}

library(maps)
library(mapsdata)
library(maptools)  #for shapefiles
library(scales)  #for transparency

map("world","Canada", xlim=c(-141,-53), ylim=c(40,85), col="gray90", fill=TRUE)
?map

```

```{r}
library(shiny)
runApp()

library(rsconnect)
deployApp()

```



```{r}

#read the google sheet
region <- read_html("https://docs.google.com/spreadsheets/d/1OxmGUNWeADbPJkQxVPupSOK5MbAECdqThnvyPrwG5Os/pub?gid=1#") %>% 
  html_nodes(xpath= "//*[@class='waffle']") %>%
  .[[2]] %>% 
  html_table(fill = TRUE)
names(region) <- c("No","Country", "Group", "ID")

# read files
gdp <- read.csv("gdppc.csv")
pop<- read.csv("population.csv")
life <- read.csv("lifeexpectancy.csv")

#change the year date
names(gdp) <- str_replace(names(gdp),"^X", "") %>%   #217
  str_replace(".0$", "")
names(pop) <- str_replace(names(pop),"^X", "") %>%   #82 . 92
  str_replace(".0$", "")
names(life)<- str_replace(names(life),"^X", "") %>%    #217
  str_replace(".0$", "")


ggdp <- gather(gdp, key=year, value = GDP.per.capita)
names(ggdp) <- c("Country", "Year", "GDP per capita")
ggdp <- ggdp[complete.cases(ggdp[,1]),]  #56160


llife <- gather(life, key=year, value = Life.expectancy.with.projections..Yellow.is.IHME)
names(llife) <- c("Country", "Year", "Life Expectancy")
llife <- llife[complete.cases(llife[,1]),]  #56160

ppop <- gather(pop, key=year, value = Total.population)
names(ppop) <- c("Country", "Year", "Total Population")   #56420
ppop <- ppop[complete.cases(ppop[,1]),]   #25025

#combine gdp and life expectancy
bb <- inner_join(ggdp, llife)
#add population in
total <- inner_join(bb,ppop)
#add region in
sum <- inner_join(region,total, by= "Country")




str(gdp) #GDP.per.capita  delete the X.  delete .0   999 obs. of  217 variables:
str(pop) #total.population  delete the X.  delete .0 delete NA.  999 obs. of  92 variables:
str(life) #Life.expectancy.with.projections..Yellow.is.IHME    999 obs. of  217 variables:



str(total)

pop[!is.na(pop),]
names(pop)
pop$NA. <- NULL
pop$NA..1 <- NULL
pop$NA..2 <- NULL
pop$NA..3 <- NULL
pop$NA..4 <- NULL
pop$NA..5 <- NULL
pop$NA..6 <- NULL
pop$NA..7 <- NULL
pop$NA..8 <- NULL
pop$NA..9 <- NULL

pop[!is.na(pop)]


#DON'T KNOW HOW TO DO WITH THIS???
ppop <- gather(pop, key=year, value = Total.population)
names(ppop) <- c("Country", "Year", "total population")
ppop <- ppop[complete.cases(ppop[,1]),]  56160



pop <- pop[complete.cases(pop[,1]),]
str(pop)
ppop <- gather(pop, key=year, value = Total.population)
names(ppop) <- c("Country", "Year", "Total Population")   #56420
ppop <- ppop[complete.cases(ppop[,1]),]   #25025
str(ppop)


str(id)

str(ppop)
str(llife)

ggdp$Country

str(ggdp)
#change the year date
names(gdp) <- str_replace(names(gdp),"^X", "") %>%   #217
  str_replace(".0$", "")
names(pop) <- str_replace(names(pop),"^X", "") %>%   #82 . 92
  str_replace(".0$", "")
names(life)<- str_replace(names(life),"^X", "") %>%    #217
  str_replace(".0$", "")


names(gdp)[names(gdp)=="GDP.per.capita"] <- "Country"
names(pop)[names(pop)=="total.population"] <- "Country"
names(life)[names(life)=="Life.expectancy.with.projections..Yellow.is.IHME"] <- "Country"

names(region)
cgdp<- inner_join(region, gdp, by = "Country")
clife <- inner_join(region, life, by = "Country")
cpop <- inner_join(region, pop, by = "Country")

str(clife)

# gather year column
demo <- gather(demo, key=year, value = GDP.per.capita)
#change name
names(demo) <- c("Country", "Year", "GDP per capita")
# as factor year
demo$Year<- as.factor(demo$Year)
#ignore NA in country
demo <- demo[complete.cases(demo[,1]),]

# write csv file
write.csv(demo, "cleaned_demographics.csv")


str(demo)

head(demo)
?gather
demo <- gather(demo, key=year, value = GDP.per.capita)
rename (demo, 'GDP.per.capita'= 'GDP per capita')

str(sum)

graph <- read_csv("cleaned_demographics.csv")
names(graph) <- c ("No", "Country", "Year", "GDP_per_capita", "Life_Expectancy", "Total_Population", "Group")


```



mtcars %>% ggvis() %>% layer_points(x = ~wt, y = ~mpg, stroke := "red")


```{r}
na.omit(subset(graph, Year== "1900")) %>% 
      ggvis () %>% 
      layer_points (x = ~GDP_per_capita, 
                    y = ~ Life_Expectancy)) %>% 
       group_by(Group)

```



```{r}

 sliderInput("integer", "Year:",
                 min=1800, max=2015, value=200,
                 animate = TRUE)



input_slider
input_slider(1800, 2015, 
                                       value = 1, 
                                       step = 1, 
                                       label = "Bandwidth adjustment")
str(graph)

1800 %in% graph$Year
subset(graph, Year = 1800)

selected_year <- input_slider(1800,2015,value=2000)   

hsb2.small[hsb2.small$id %in% c(12, 48, 86, 11, 20, 195), ])

subset(graph, Year == selected_year)

selected_year = 2000
na.omit(subset(graph, Year == selected_year)) %>% 
      ggvis () %>% 
      layer_points (x = ~GDP_per_capita, 
                    y = ~ Life_Expectancy,
                    fill = ~ Group)   
    %>% 
      
 
    mtcars %>% ggvis(x = ~wt) %>%
       
layer_densities(
      adjust = input_slider(1800, 2015, value = 1, step = 1, label = "Bandwidth adjustment")
```


```{r}
na.omit(subset(graph, Year== 2015)) %>% 
      ggvis () %>% 
      layer_points (x = ~GDP_per_capita, 
                    y = ~ Life_Expectancy,
                    fill = ~ Group,
                    size = ~ Total_Population)
```

```{r}

    selected_year <- input_slider(1800,2015,2000, label = "Year")

    na.omit(subset(graph, Year == selected_year)) %>% 
      ggvis () %>% 
      layer_points (x = ~GDP_per_capita, 
                    y = ~ Life_Expectancy,
                    fill = ~ Group,
                    size = ~ Total_Population,
                    opacity := input_slider(0.5, 1, 0.5,
                                       label = 'Point Opacity'))
    
    %>% 
      layer_smooths(span = input_slider(0.5, 1, 0.5,
                                    label = 'Species Models'),
                fill = ~Group, se=TRUE)
```


```{r}
iris %>%
  # the ggvis function, now set the axis
  ggvis(~Sepal.Width, ~Sepal.Length) %>%
  # add the smoother for all points
  layer_smooths(span = input_slider(0.5, 1, 0.5,
                                    label = 'General Model'),
                se = TRUE) %>%
  # now group by species
  group_by(Species) %>%
  # add points per species and colour them
  layer_points(size := input_slider(10, 200, 50,
                                    label = 'Point Size'),
               opacity := input_slider(0.5, 1, 0.5,
                                       label = 'Point Opacity'),
               fill = ~Species) %>%
  # now add smoothers per species and colour them
  layer_smooths(span = input_slider(0.5, 1, 0.5,
                                    label = 'Species Models'),
                fill = ~Species, se=TRUE) %>%
  # add new labels
  add_axis("x", title = "Sepal Width") %>%
  add_axis("y", title = "Sepal Length") %>% 
  add_tooltip(iris$Sepal.Length, "hover")
```



```{r}
na.omit(subset(graph, Year== 2000)) %>% 
      ggvis (x = ~GDP_per_capita, 
             y = ~ Life_Expectancy) %>% 
      layer_points (fill = ~ Group,
                    size = ~ Total_Population,
                    opacity : = )%>% 
      add_axis("x", title = "GDP Per Capita (Inflation-Adjusted)") %>%
      add_axis("y", title = "Life Expectancy Birth",
               values = c(25, 50, 75))

      #guides (size = FALSE, alpha = FALSE)  %>% 
```



```{r}
?add_tooltip
```












