---
title: "Lab1"
author: "Shangjun Jiang"
date: " June 7 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
scored <- c(14, 14, 9, 14, 28, 13, 13, 24, 17, 6, 24, 0, 24, 13, 26, 14)
against <- c(19, 30, 16, 38, 31, 24, 23, 30, 41, 13, 20, 52, 13, 31, 24, 47)

# PART 1
# 1. How many points did the Raiders score in game 7?
```{r}
scored [7]
```

# 2. What was the score of the first 5 games?
```{r}
scored [seq(1:5)]
scored [c (1,2,3,4,5)]
```

# 3. What were the scores of the even games? Try to do this problem without typing in c(2,4,…)

seq (from = 2, to = length(scored), by = 2)
scored [seq (from = 2, to = length (scored), by =2)]
```{r}
scored [seq (2,(length(scored)), 2)]
```

# 4. What was the score of the last game? Try to do this problem without typing in the number of the last game.

```{r}
scored [length (scored)]
tail (scored, 1)
```

# 5. Select the scores higher than 14.

```{r}
scored [scored > 14]
```

# 6. Select the scores equal to 14.

```{r}
scored [scored == 14]
```

# 7. Select the scores equal to 13 or 14.

```{r}
scored [scored == 13 | scored == 14]
scored [scored %in% c (13, 14)]
```

# 8. Select the scores between between 7 and 21 points.

```{r}
scored [scored >7 & scored < 21]
```

# 9. Sort the scores in decreasing order.
sort (scored, decreasing = TRUE)
```{r}
sort (scored, decreasing = T)
```

# 10. What was the highest score achieved?

```{r}
max (scored)
```


# 11. What was the lowest score achieved?

```{r}
min (scored)
```

# 12. What was the average score?

```{r}
mean (scored)
```

# 13. Use the summary() function to give some summary statistics.

```{r}
summary (scored)
```

# 14. In how many games did the Raiders score over 20 points?
length (scored [TRUE == (scored > 20)])
length (which (scored > 20))
length (scored [scored >20])
```{r}
length (scored [scored >20])
```


# PART 2
# 1. What was the sum of the scores in game 7?
scored [7] + against [7]
```{r}
scored [7] + against [7]
```

# 2.What was the sum of the scores in the last 5 games?
length (scored)
length (against)
scored [12:16]+ against [12: 16]
```{r}
(scored + against) [seq (length (scored) - 4, length (scored))]
```

# 3. What was the difference in scores in the odd games?
sum (scored [c (1,3,5,7,9,11,13,15)] - against [c (1,3,5,7,9,11,13,15)])
abs (scored [seq (from =1, to = length (scored), by =2)] - against [seq (from = 1, to = length (against), by = 2)])
```{r}
abs (scored - against) [seq (1, length (scored), 2)]
abs (scored [seq (from =1, to = length (scored), by =2)] - against [seq (from = 1, to = length (against), by = 2)])
?abs
```


# 4. Which games did the Raiders win?

```{r}
which (scored > against)
idx <- seq (1, length (scored))
idx [scored >against]
```

# 5. Were there any ties?
which (scored == against)
```{r}
any (scored == against)
```


