---
title: "Good Coding Practices"
author: "Andrew Do"
date: "July 12, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sol = TRUE
```

## Short Exercises
Rewrite the following according to our class style guide:

1.
```{r, eval = FALSE}
x < - c( NA,1,-2,3,-4,5 )
  y<-3
  y<-x * - 1
  y[ y>0 ]
```

```{r, echo = sol}
# <Your fix here>
x_vector <- c(NA, 1, -2, 3, -4, 5)
y <- 3
y <- x_vector * - 1
y [y > 0]
```

2. 
```{r}
mean <- function(x) {
sum (x)/length( x )
}
```

```{r, echo = sol}
# <Your fix here>
mean <- function(x) {
  sum (x) /length (x)
}
```

3. 
```{r}
library( ggplot2 )
second_version_of_mpg <- mpg[ mpg$cyl == 6,]
second_version_of_mpg$class <- as.character(second_version_of_mpg$class)
ggplot(data=second_version_of_mpg,aes(cty,hwy,color=class))+geom_point()+geom_smooth( method = "lm", se=FALSE ) + labs (title="City vs. Highway MPG" )
```

```{r, echo = sol}
# <Your fix here>
library(ggplot2)

second_version_of_mpg <- mpg[mpg$cyl == 6, ]
second_version_of_mpg$class <- as.character(second_version_of_mpg$class)

ggplot(data=second_version_of_mpg,aes(cty,hwy,color=class)) +
  geom_point() +
  geom_smooth(method = "lm", se=FALSE) + 
  labs(title="City vs. Highway MPG")
```

## Longer Exercises

Fix the following code with the following goals:

* Readability - an untrained person should be able to guess what's going on
    + Use meaningful names
    + Use whitespace to make the code flow
    + Provide documentation
    + Use functions from the packages we've covered (they're designed to be readable!)
  
* Compactness - do not be more verbose than you have to be
    + Think of ways to vectorize the function
    + Avoid copy-paste
    + Use the `lapply` family
    + Modularize your code (small functions instead of massive ones)
  
* Usable as intended
    + If necessary, include error messages
    + Don't force the user to rely on implicit coercion
    + Output the intentional data type

### Exercise 1
Infer what the function `d` is doing and rewrite it according to our class style guide.  Include documentation so that future users won't have to decipher the code.
```{r}

d <- function(f, x, y, s) {
  stuff<-seq(x,y,by=s)
  stuff2<-c()
  for(i in 1:length(stuff)){thing<-f(stuff[i]); stuff2[i]<-thing}
  m<-max(stuff2)
  mm<-stuff[stuff2==m]
  mm<-min(mm)
  return(list(m,mm))
}

# Example usage
g <- function(x) -(x ^ 2)
d(g, -1, 1, .1)
```

```{r, echo = sol}
# <Your fix here>
d <- function(f, x, y, s) {
  stuff <- seq(x, y, by=s)
  #create an empty vector
  stuff2 <- c()
  
  #apply the function to the list
  for(i in 1:length(stuff)){
    thing <- f(stuff[i]); 
    stuff2[i] <- thing 
    }
  
  #get the max after applying the function
  stuff2_max <- max(stuff2)
  #find the max in the original vector
  stuff_v <- stuff[stuff2==stuff2_max]
  #get the min from the original vector
  stuff_v <- min(stuff_v)
  
  #return the list of (max of changed vector) and the() min of the original vector)
  return(list(stuff2_max,stuff_v))
}

# Example usage
g <- function(x) {
  x ^ 2
}
d(g, -1, 1, .1)

```


### Exercise 2
Figure out what the `ss` function is doing, rewrite it so it uses more expressive functions according to our style guide.  Provide documentation.
```{r}
ss <- function(x) 
{x<-x[!is.na(x)]
a<-x[1];for(i in 2:length(x)) a[i]<-(a[i-1]+x[i])
a<-a/(1:length(x))
foo<-x
cc<-0
for(i in 1:length(foo)){x<-foo[1:i]
c<-sort(x);
if(length(x)%%2==0){cc[i]<-(c[floor((length(c)+1)/2)] + c[ceiling((length(c)+1)/2)])/2} else{ cc[i]<-c[(length(c)+1)/2]}}
return(list(a,cc))
}

# Example usage
ss(c(5,10,15,20,5,10,15,20))
ss(1:10)
ss(c(1,2,6,2,4,5))
```

```{r, echo = sol}
# <Your fix here>
ss <- function(x) {
  x <- x [!is.na(x)]
  float_x <- x[1];
  
  #get the mean of the added_item 
  for (i in 2:length(x)) 
    float_x[i] <- (float_x[i-1] + x[i])
  
  float_x <- float_x / (1:length(x))
  foo <- x
  simplified_x <- 0

  for (i in 1:length(foo)) {
    x <- foo[1:i]
    c <- sort(x);
    if (length(x) %% 2 == 0 ) {
      simplified_x[i] <- (c[floor((length(c) + 1) / 2)] + 
                          c[ceiling((length(c)+1) / 2)]) / 2
      } 
    else{ 
      simplified_x[i]<-c [(length(c) + 1) / 2]
    }
  }
  return(list(float_x,simplified_x))
}

ss(c(5,10,15,20,5,10,15,20))
ss(1:10)
ss(c(1,2,6,2,4,5))

```

### Exercise 3
Rewrite the following script in a more compact form using packages we've covered in this class.  It shouldn't take more than 7 function calls---3 if you took the time to read the `dplyr` vignette!
```{r}
d<-iris
dd<-unique(d[,5])
d1<-d[which(d[,5]==dd[1]),]
d2<-d[which(d[,5]==dd[2]),]
d3<-d[which(d[,5]==dd[3]),]
d1[,1] <- mean(d1[,1])
d1[,2] <- mean(d1[,2])
d1[,3] <- mean(d1[,3])
d1[,4] <- mean(d1[,4])
d2[,1] <- mean(d2[,1])
d2[,2] <- mean(d2[,2])
d2[,3] <- mean(d2[,3])
d2[,4] <- mean(d2[,4])
d3[,1] <- mean(d3[,1])
d3[,2] <- mean(d3[,2])
d3[,3] <- mean(d3[,3])
d3[,4] <- mean(d3[,4])
ddd<-rbind(d1[1,],d2[1,],d3[1,])
rownames(ddd) <- NULL

ddd
str(d)
dd
d[,5]

```

```{r, echo = sol}
library(dplyr)
# <Your fix here>
df <- iris
#mean_df <- df %>% 
#  group_by(Species) %>% 
#  summarise_each(funs(mean))

mean_df <- summarise_each(
              group_by(df, 
                       Species), 
              funs(mean))
mean_df <- mean_df[c(2,3,4,5,1)]
mean_df

```

## Remote Computing Practice
Upload the `.rmd` file to `Documents/lab19/` on your server account and knit it using the command line. Submit the `.html` file produced by knitting on the server.  Assuming you're in the folder with the markdown file on the server, the command is:

```{sh, eval = FALSE}
Rscript -e "rmarkdown::render('lab19.Rmd')"
```


```{r, echo = sol}
sessionInfo()
```

